---
title: "FNMOC Products"
subtitle: "Model Data"
format:
  html:
    toc: true
    toc-depth: 5
    grid:
      body-width: 1200px
---

```{r}
#| echo: false
#| message: false
library(tidyverse)
library(jsonlite)

data <- fromJSON("data/fnmoc_list.json", simplifyDataFrame = TRUE)

model_data <- data %>% unnest(items, names_sep = "_") %>%
  filter(items_title == "FNMOC Cross-Model Long Time Series") %>%
  unnest(items_items, names_sep = "_")

```

## FNMOC Model Data

**Mean Sea Level Pressure**

ERD has been acquiring FNMOC operational gridded model output since 1948. Due to improvements in model development and increases in computational power and storage capacity, the FNMOC models and their pressure field output changed resolution over time (table below). From 1948 to 1967, data were provided on paper as monthly means.  Subsequently ERD has maintained a relationship with FNMOC and obtained daily downloads of 6-hourly model forecasts.


```{=html}
<table border=1 cellpadding=2><tr><td><b> Years </b></td><td><b>Projection</b></td><td><b>Coverage</b></td><td><b>Resolution</b></td></tr><tr><td>1967 - 1980</td><td> 63 x 63 polar stereographic</td><td>Northern Hemisphere</td><td> about 3&#176; latitude</td></tr><tr><td>1981 - 1996</td><td> 73 x 144 spherical </td><td>global</td><td>2.5&#176;</td></tr><tr><td>1996 - present</td><td>360x181 spherical</td><td>global</td><td>1&#176;</td></tr></table>
```

ERD seeks to maintian long consistent time series of air/ocean indices for use in climate studies despite change in models and model resolution. The cross-model time series represents the longest possible 6-hourly series of FNMOC Mean Sea Level pressure. It has been interpolated across models to a consistent 1-degree grid for use in calculating environmental indices.

**Surface Wind and Geopotential Height**

Cross-Model output of surface wind and geopotential height since 1997 are also provided below.  At the time of development, the surface wind model output was not deemed as reliable for computation of upwelling index as the geostropic winds calculated from sea level pressre.  For this reason, and in order to provide consistency in the calculation, Bakun upwelling index calculated by ERD always uses sea level pressure.

**Recent Model Data**

Links to recent FNMOC NAVGEM and NOGAPS model output are also provided below.

## FNMOC Cross-Model Long Time Series

Longest possbile time series generated by interpolating to a 1-degree grid across various models and model resolutions described above.
```{r, results = 'asis'}
#| echo: false
#| message: false
#| eval: true
section_data <- function(model_data){
var_dsets <- model_data$items_items_title
for (v in 1:length(var_dsets)){
var1 <- var_dsets[v]
slp <- model_data %>% filter(items_items_title == var1) %>%
  unnest(items_items_items, names_sep = "_")
dsets <- slp %>% unnest(items_items_items_items, names_sep = "_")

cat("\n\n### ",var1, "\n\n",sep="")
 for (i in 1:nrow(slp)){
  cat("* **",slp$items_items_items_tres[i],",    ",slp$items_items_items_tspan[i], "**\n\n",sep="")
   cat("   + 1-degree,  0 to 360  <a href='https://coastwatch.pfeg.noaa.gov/erddap/griddap/",dsets$items_items_items_items_erddset[i*2-1],".html' target='_blank'>ERDDAP download</a>\n\n",sep="")
   cat("   + 1-degree,  -180 to 180  <a href='https://coastwatch.pfeg.noaa.gov/erddap/griddap/",dsets$items_items_items_items_erddset[i*2],".html' target='_blank'>ERDDAP download</a>\n\n",sep="")
}
}
}

section_data(model_data)
```


## Navy Operational Global Atmospheric Prediction System (NOGAPS)

NAVGEM (see below) replaced NOGAPS in [2013](https://en.wikipedia.org/wiki/Navy_Operational_Global_Atmospheric_Prediction_System).


## Navy Global Environmental Model (NAVGEM)

2013 - present

```{r, results = 'asis'}
#| echo: false
#| message: false
#| eval: true
model_data2 <- data %>% unnest(items, names_sep = "_") %>%
  filter(items_title == "Navy Global Environmental Model (NAVGEM)") %>%
  unnest(items_items, names_sep = "_")
section_data(model_data2)

```
