---
title: "FNMOC Products"
subtitle: "Model-Derived Products"
format:
  html:
    toc: true
    toc-depth: 5
    grid:
      body-width: 1200px
---


```{r}
#| echo: false
#| message: false
library(tidyverse)
library(jsonlite)

data <- fromJSON("data/fnmoc_list.json", simplifyDataFrame = TRUE)

model_data_prod <- data %>% filter(title =="Derived Products") %>% unnest(items, names_sep = "_")

```

## FNMOC Model-Derived Products

The products below are derived from the time series of FNMOC Cross-Model mean sea level pressure described under [FNMOC models](/products/fnmoc/model.html) and are calculated as described in the [Bakun Upwelling Index](/projects/upwelling/bakun.html) section

```{r, results = 'asis'}
#| echo: false
#| message: false
#| eval: true
section_data_prod <- function(model_data){
var_dsets <- model_data$items_title
for (v in 1:(length(var_dsets)-1)){
var1 <- var_dsets[v]
vars1 <- model_data %>% filter(items_title == var1) %>%
  unnest(items_items, names_sep = "_")
dsets <- vars1 %>% unnest(items_items_items, names_sep = "_")
erdsets <- dsets %>% unnest(items_items_items_items, names_sep = "_")

cat("\n\n### ",var1, "\n\n",sep="")
 for (i in 1:nrow(dsets)){
  cat("* **",dsets$items_items_items_tres[i],",    ",dsets$items_items_items_tspan[i], "**\n\n",sep="")
   cat("   + 1-degree,  0 to 360  <a href='https://coastwatch.pfeg.noaa.gov/erddap/griddap/",erdsets$items_items_items_items_erddset[i*2-1],".html' target='_blank'>ERDDAP download</a>\n\n",sep="")
   cat("   + 1-degree,  -180 to 180  <a href='https://coastwatch.pfeg.noaa.gov/erddap/griddap/",erdsets$items_items_items_items_erddset[i*2],".html' target='_blank'>ERDDAP download</a>\n\n",sep="")
}
}
}

section_data_prod(model_data_prod)
```

## Monthly Sea Level Pressure Maps

Monthly mean pressure maps based on the FNMOC 360x181 (1-degree) analyzed fields.

```{ojs}
//| echo: false
d = new Date();
startYear = 1997;
currentYear = d.getMonth() === 0 ? d.getFullYear() - 1 : d.getFullYear()
thismon = d.getMonth() // 1-based index matching your months array

// Create arrays
years = Array.from({ length: currentYear - startYear + 1 }, (_, index) => startYear + index)
months = Array.from({ length: 12 }, (_, index) => 0 + index)
```


```{ojs}
//| echo: false
// Render the dropdown menu
viewof selectedFile5 = Inputs.select(years, {value: currentYear,label: "Choose Year",
  format: x => x.toString(), width:100 })
html`<br>`
viewof selectedFile6 = Inputs.select(months, {value: thismon, label: "Choose Month",format: m => new Date(2000, m - 1, 1).toLocaleString("en-US", { month: "short" }), width:100})

```

```{ojs}
//| echo: false
// Construct the final download URLs
baseUrl5 = "https://oceanwatch.pfeg.noaa.gov/products/PFEL/modeled/pressure_maps/"
selectedMonthName = new Date(2000, selectedFile6 - 1, 1).toLocaleString("en-US", { month: "short" }).toLowerCase()
filename = selectedMonthName+selectedFile5.toString().substr(2)+"_Pmsl.gif";
downloadUrl5 = baseUrl5 + filename 

```


```{ojs}
//| echo: false
// Render the HTML download links
html`<img src="${downloadUrl5}" /><br><a href="${downloadUrl5}" target="_blank">download image</a>`
```

